---
title: "Forecasting Real Housing Price Returns of the United States Jo using Machine Learning: The Role of Climate Risks"
format:
  html:
    theme:
      light: cerulean
      dark: slate  
    smaller: true
    lang: pt-br
    embed-resources: true
    html-math-method: katex
    self-contained-math: false
---

<div style="text-align: justify">

<style>
body {
text-align: justify}
</style>


```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false

library(quarto)
library(tidyverse)
library(exams)
library(knitr)
library(kableExtra)
library(openxlsx)

# Auxiliar files

rm(list = ls())

source("functions_results.r")
```

# Forecasting approach

## Inicial parameters

```{r}
# Models, forecast horizons and lags

ind_models <- 1:6 # models from m1 to m6
n_lags <- 48 # number of lags
pad <- TRUE # standardization
for_hor_can <- c(1, seq(from = 6, to = 48, by = 6))
n_windows <- 516 # out-of-sample size
```

```{r, quarto_file_gen}
#| echo: false
#| eval: false

out_file_name <- paste(
  f_model_name_results(ind_models, n_lags, for_hor_can, n_windows, pad),
  ".html",
  sep = ""
)

quarto::quarto_render(
  input = "results.rmd",
  output_format = "html",
  output_file = out_file_name
)
```


- The forecasting approach can be view as a L2-boosting method applied to an AR-direct (plus exogenous variables) model:
$$
  y_{t} = \beta_0 + \beta_h y_{t-h} + \cdots \beta_{h+`r n_lags`} y_{t-h-`r n_lags`} + \vec{x}_{t-h}^{\intercal} \vec{\delta}_{h} + \cdots + \vec{x}_{t-h-`r n_lags`}^{\intercal} \vec{\delta}_{h+`r n_lags`},
$$
where $\vec{x}$ contains the *exogenous* regressors.
- Note that we allow for `r n_lags` lags for each variable.
- We consider $h = `r paste(for_hor_can, sep = "", collapse = ", ")`.$

# Results

```{r}
#| echo: false

list_workspace <- vector(mode = "list", length = length(for_hor_can))
names(list_workspace) <- paste("h", for_hor_can, sep = "")

for (i in seq_along(for_hor_can)) {
  for_hor <- for_hor_can[i]

  file_name_load <- paste(
    "../h",
    for_hor,
    "/",
    f_model_name(ind_models, n_lags, for_hor, n_windows, pad),
    ".rda",
    sep = ""
  )

  load(file_name_load)

  list_workspace[[i]] <- list(
    var_imp_list = var_imp_list,
    forecast_mat = forecast_mat,
    csfe_mat = csfe_mat,
    y_out = y_out
  )
}
```

## RMSE

- The table below presents the RMSE for the six models considered for each forecast horizon.
- Values in blue denote the lowest RMSE for each forecast horizon.

```{r}
#| echo: false

rmse_table <- matrix(NA, nrow = length(for_hor_can), ncol = length(ind_models))

colnames(rmse_table) <- paste("m", ind_models, sep = "")
rownames(rmse_table) <- paste("h", for_hor_can, sep = "")

for (i in seq_along(for_hor_can)) {

  rmse_table[i, ] <- apply(
    X = list_workspace[[i]]$forecast_mat,
    MARGIN = 2,
    FUN = f_rmse,
    y = y_out
  )

}

rmse_table_kable <- rmse_table %>%
  round(4) %>%
  t() %>%
  as.data.frame() %>%
  mutate(
    across(
      everything(),
      ~cell_spec(
        .x,
        color = ifelse(
          .x == min(.x),
          "blue",
          "black"
        )
      )
    )
  )

kable(rmse_table_kable)

# Saving

openxlsx::write.xlsx(
  x = data.frame(t(rmse_table)),
  file = "../Tables/xlsx/rmse_table.xlsx",
  asTable = TRUE,
  rowNames = TRUE,
  colNames = TRUE
)

write.csv(
  x = data.frame(t(rmse_table)),
  file = "../Tables/csv/rmse_table.csv"
)
```

## Variable Selection

```{r}
#| echo: false

n_imp_var <- 15
```

- The tables below show the `r n_imp_var` most frequently selected variables for each forecast horizon.

```{r, results="asis", scale = 0.3}
#| echo: false

f_most_sel <- function(x) {
  res <- paste(
    names(x), " ",
    round(100 * x, 2), "%",
    sep = ""
  )
  return(res)
}

f_most_sel_table <- function(for_hor) {

  i <- which(for_hor_can == for_hor)

  var_sel_table <- matrix(
    data = NA,
    nrow = n_imp_var,
    ncol = length(ind_models)
  )
  colnames(var_sel_table) <- paste("m", ind_models, sep = "")
  rownames(var_sel_table) <- paste(seq_len(n_imp_var))

  for (k in seq_along(ind_models)) {

    mat_var_imp_aux <- list_workspace[[i]]$var_imp_list[[k]]

    mat_sel_aux <- matrix(
      data = NA,
      nrow = length(mat_var_imp_aux),
      ncol = length(mat_var_imp_aux[[1]])
    )

    colnames(mat_sel_aux) <- names(mat_var_imp_aux[[1]])

    for (j in seq_along(mat_var_imp_aux)) {
      mat_sel_aux[j, ] <- as.numeric(mat_var_imp_aux[[j]] != 0)
    }

    most_sel_var <- apply(mat_sel_aux, 2, mean) %>% sort(decreasing = TRUE)

    var_sel_table[, k] <- f_most_sel(most_sel_var)[1:n_imp_var]
  }
  return(var_sel_table)
}

for (i in for_hor_can) {
  kable(
    x = f_most_sel_table(i),
    caption = paste("H = ", i, sep = "")
  ) %>%
    print() %>%
    cat("\n")
}
```

```{r, echo=FALSE}
f_most_sel_exp <- function(x) {
  res <- c(
    paste(names(x)),
    paste(round(100 * x, 2), "%", sep = "")
  ) %>% matrix(nrow = 2, byrow = TRUE) %>% as.vector()
  return(res)
}

f_most_sel_table_exp <- function(for_hor) {

  i <- which(for_hor_can == for_hor)

  var_sel_table <- NULL

  for (k in seq_along(ind_models)) {

    mat_var_imp_aux <- list_workspace[[i]]$var_imp_list[[k]]

    mat_sel_aux <- matrix(
      data = NA,
      nrow = length(mat_var_imp_aux),
      ncol = length(mat_var_imp_aux[[1]])
    )

    colnames(mat_sel_aux) <- names(mat_var_imp_aux[[1]])

    for (j in seq_along(mat_var_imp_aux)) {
      mat_sel_aux[j, ] <- as.numeric(mat_var_imp_aux[[j]] != 0)
    }

    most_sel_var <- apply(mat_sel_aux, 2, mean) %>% sort(decreasing = TRUE)

    var_sel_table <- cbind(
      var_sel_table,
      (
        f_most_sel_exp(most_sel_var) %>%
          matrix(ncol = 2, byrow = TRUE)
      )[1:n_imp_var, ]
    )
  }

  colnames(var_sel_table) <- c(
    paste(
      paste("m", rep(ind_models, each = 2), sep = ""),
      c("_name", "_freq"),
      sep = ""
    )
  )
  rownames(var_sel_table) <- paste(seq_len(n_imp_var))

  return(var_sel_table)
}

# Loop

list_xlsx <- vector(mode = "list", length = length(for_hor_can))
names(list_xlsx) <- paste("hor_", for_hor_can, sep = "")

for (i in seq_along(for_hor_can)) {
  kable(
    x = f_most_sel_table_exp(for_hor_can[i]),
    caption = paste("H = ", for_hor_can[i], sep = "")
  ) %>%
    print() %>%
    cat("\n")

  # Saving

  list_xlsx[[i]] <- f_most_sel_table_exp(for_hor_can[i]) %>% data.frame()

  write.csv(
    x = f_most_sel_table_exp(for_hor_can[i]),
    file = paste(
      "../Tables/csv/",
      "most_sel_variables_table_hor_",
      for_hor_can[i],
      ".csv",
      sep = ""
    )
  )
}

# Saving

openxlsx::write.xlsx(
  x = list_xlsx,
  file = paste(
    "../Tables/xlsx/",
    "most_sel_variables_table",
    ".xlsx",
    sep = ""
  ),
  sheetName = paste("hor_", for_hor_can, sep = ""),
  asTable = TRUE,
  rowNames = TRUE,
  colNames = TRUE
)

```

## MCS

```{r}
#| echo: false

library(MCS)

f_mcs_table <- function(mcs_obj, model_name) {
  obj_names <- mcs_obj@Info$model.names
  obj_table_m <- mcs_obj@show[, "Rank_M", drop = FALSE]
  obj_table_r <- mcs_obj@show[, "Rank_R", drop = FALSE]

  res <- matrix(NA, nrow = length(model_name), ncol = 2)
  colnames(res) <- c("Rank_M", "Rank_R")
  rownames(res) <- model_name

  res[obj_names, "Rank_M"] <- obj_table_m[obj_names, 1]
  res[obj_names, "Rank_R"] <- obj_table_r[obj_names, 1]

  eliminated_models <- which(!(model_name %in% obj_names))
  res[eliminated_models, ] <- "E"

  return(res)
}

mcs_table_m <- matrix(NA, nrow = length(ind_models), ncol = length(for_hor_can))
rownames(mcs_table_m) <- paste("m", ind_models, sep = "")
colnames(mcs_table_m) <- paste("h", for_hor_can, sep = "")
mcs_table_r <- mcs_table_m

for (i in seq_along(for_hor_can)) {

  mcs_aux <- apply(
    X = list_workspace[[i]]$forecast_mat,
    MARGIN = 2,
    FUN = LossLevel,
    realized = list_workspace[[i]]$y_out,
    which = "SE"
  )

  mcs_test <- MCSprocedure(
    Loss = mcs_aux,
    alpha = 0.15,
    B = 5000,
    cl = NULL,
    ram.allocation = TRUE,
    statistic = "Tmax",
    k = 10,
    verbose = FALSE
  )

  model_name <- colnames(list_workspace[[i]]$forecast_mat)
  mcs_table_aux <- f_mcs_table(mcs_test, model_name)
  mcs_table_m[, i] <- mcs_table_aux[, "Rank_M"]
  mcs_table_r[, i] <- mcs_table_aux[, "Rank_R"]
}

kable(mcs_table_m, caption = "Rank M")
kable(mcs_table_r, caption = "Rank R")

# Saving

openxlsx::write.xlsx(
  x = list(
    data.frame(mcs_table_m),
    data.frame(mcs_table_r)
  ),
  file = paste(
    "../Tables/xlsx/",
    "mcs_tables",
    ".xlsx",
    sep = ""
  ),
  sheetName = paste("rank_", c("m", "r"), sep = ""),
  asTable = TRUE,
  rowNames = TRUE,
  colNames = TRUE
)


write.csv(
  x = mcs_table_m,
  file = paste(
    "../Tables/csv/",
    "mcs_m_table",
    ".csv",
    sep = ""
  )
)

write.csv(
  x = mcs_table_r,
  file = paste(
    "../Tables/csv/",
    "mcs_r_table",
    ".csv",
    sep = ""
  )
)

```

## GW test

- Now, we apply the GW-test relative to the $m1$ model.
  - Relative RMSE smaller than 1 and p-value smaller than 0.05 implies that the competing model statistically outperforms the benchmark model.
  - Relative RMSE greater than 1 and p-value smaller than 0.05 implies that the benchmark model statistically outperforms its competitor model.
  - A p-value greater than 0.05 means that the differences with respect to predictive performance between the benchmark and the competing model are not statistically significant.

```{r, echo=FALSE}

gw_p_value_mat <- matrix(
  data = NA,
  nrow = length(ind_models) - 1,
  ncol = length(for_hor_can)
)
colnames(gw_p_value_mat) <- names(list_workspace)
rownames(gw_p_value_mat) <- paste("m", 2:6, sep = "")
rel_rmse_mat <- gw_p_value_mat

for (i in seq_along(for_hor_can)) {

  # Relative RMSE

  rel_rmse_mat[, i] <- rmse_table[i, -1] / rmse_table[i, 1]

  # GW-test

  other_pred <- list_workspace[[i]]$forecast_mat[, -1] %>% as.matrix()
  bench_pred <- list_workspace[[i]]$forecast_mat[, 1]
  y_real <- list_workspace[[i]]$y_out

  for (j in seq_len(length(ind_models) - 1)) {

    gw_p_value_mat[j, i] <- gw.test(
      x = bench_pred,
      y = other_pred[, j],
      p = y_real,
      T = 721,
      tau = 1,
      method = "HAC",
      alternative = "two.sided"
    )$p.value
  }
}

kable(
  x = rel_rmse_mat,
  caption = "RMSE - Relative to the $m1$ model",
  digits = 3,
  align = "c",
  format.args = list(
    nsmall = 3,
    signif(3)
  )
)

gw_p_value_table <- gw_p_value_mat %>%
  round(4) %>%
  format(
    digits = 3,
    nsmall = 3,
    scientific = FALSE
  ) %>%
  f_color_aux(x = ., y = rel_rmse_mat)

kable(
  x = gw_p_value_table,
  caption = "GW two-sided test (p-value) - Relative to the $m1$ model",
  digits = 3,
  align = "c"
) %>%
  add_footnote(
    label = c(
      text_spec(
        x = "Competing model statistically outperforms the benchmark model.",
        color = "blue"
      ),
      text_spec(
        x = "The benchmark model statistically outperforms its competitor.",
        color = "red"
      ),
      text_spec(
        x = "The difference between the benchmark and the competing model are not statistically significant.",
        color = "black"
      )
    ),
    notation = "number",
    threeparttable = TRUE
  )



kable(
  x = gw_p_value_mat,
  caption = "GW two-sided test (p-value) - Relative to the $m1$ model",
  digits = 3,
  align = "c",
  format.args = list(
    nsmall = 3,
    signif(3)
  )
)

# Saving

openxlsx::write.xlsx(
  x = list(
    data.frame(rel_rmse_mat),
    data.frame(gw_p_value_mat)
  ),
  file = paste(
    "../Tables/xlsx/",
    "gw_test_tables",
    ".xlsx",
    sep = ""
  ),
  sheetName = c("rel_rmse", "p_value"),
  asTable = TRUE,
  rowNames = TRUE,
  colNames = TRUE
)


write.csv(
  x = rel_rmse_mat,
  file = paste(
    "../Tables/csv/",
    "gw_test_rel_rmse",
    ".csv",
    sep = ""
  )
)

write.csv(
  x = gw_p_value_mat,
  file = paste(
    "../Tables/csv/",
    "gw_test_p_value",
    ".csv",
    sep = ""
  )
)
```